
%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNH}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\resumeSubHeadingListStartBullets}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\usepackage{array}
\makeatletter
\newcommand\HUGE{\@setfontsize\Huge{38}{47}} 
\newcolumntype{L}{>{\hb@xt@\z@\bgroup}l<{\hss\egroup}}
\newcolumntype{C}{>{\centering\arraybackslash}c}
\newcolumntype{R}{>{\hb@xt@\z@\bgroup\hss}r<{\egroup}}
\makeatother

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{L@{\extracolsep{\fill}}C@{\extracolsep{\fill}}R}
  \href{mailto:email@gatech.edu}{email@gatech.edu} &
  \multirow{2}{*}{\Huge \textbf{John Smith}} &
  \href{https://personal-website.com}{https://personal-website.com} \\
  (123) 456-7890 & & US Citizen
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education }
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {B.S. \& M.S. in Computer Science, GPA: 3.9/4.0}{Aug 2018 -- May 2022}
      \resumeItemListStart
        \resumeItem{Concentrations}{Machine Learning \& Information Internetworks}
        \resumeItem{Coursework}
          {Data Structures \& Algorithms, Object-Oriented Programming, Objects \& Software Design, Computer Organization,  Systems \& Networks, Design of Algorithms, Database Systems, Statistics, Applied Combinatorics}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
      {NCR Corporation}{Atlanta, GA}
      {Software Engineering Intern}{Jun 2020 -- Aug 2020}

      \resumeItemListStart
        \resumeItemNH{Developed a new natural language processing feature for the Apiary malware analysis framework.}
        \resumeItemNH{Created new web-pages, RESTful API-endpoints and search features to better display results to users.}
        \resumeItemNH{Interfaced with MongoDB and Elasticsearch databases to access data, prototype new scripts and store results.}
        \resumeItemNH{Wrote extensive unit tests to ensure future functionality and updated Docker files for smarter deployment.}
      \resumeItemListEnd
    \resumeSubheading
      {Georgia Tech Research Institute}{Atlanta, GA}
      {Research Assistant}{May 2019 -- Dec 2019}
      \resumeItemListStart
        \resumeItemNH{Wrote novel algorithms to create 3D visualizations of the seafloor using LiDAR data collected from a plane.}
        \resumeItemNH{Developed new display features for a proprietary 3-D data visualization software, using C++.}
        \resumeItemNH{Compiled my results and submitted a paper to the SPIE DCS academic conference.}
      \resumeItemListEnd
    \resumeSubheading
      {NASA Glenn Research Center}{Cleveland, OH}
      {Research Assistant}{May 2018 -- Jun 2018}
      \resumeItemListStart
        \resumeItemNH{Tested a machine learning algorithm's memory usage in a Arduino by training a small car to avoid obstacles.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStartBullets
    \resumeSubItem{CS4400 Group Project: Food Truck Webapp}
      {A webapp used for organizing Food Trucks. Designed the SQL database schema, including details about location, menu and customer data. Built the backend using Node.js, Express and MySQL. Used React.js and bootstrap to create an appealing frontend.}
    \resumeSubItem{HackGT Hackathon Project: ``Alexa Freestyle"}
      {Used a song lyric API and deep machine learning to generate new songs from existing lyrics. Connected Alexa to Amazon Web Service's ``Lambda" service to handle user requests and exceptions. Utilized an AWS ``EC2" instance to host a Flask server to run our algorithm efficiently and cache results.}
    \resumeSubItem{CS2340 Group Project: ``RISK"}
      {A multiplayer webapp version of the boardgame ``RISK". Built the front-end with Vue.js and Bootstrap. Used a Websocket API to connect to a Play Framework backend.}
  \resumeSubHeadingListEnd
  
%-----------EXTRACURRICULARS-----------------
\section{Involvement}
  \resumeSubHeadingListStartBullets
    \resumeSubItem{Georgia Tech Automotive Research Lab}
      {Software Team Lead for the student lead autonomous car research group. Managed a team of eight students in completing software tasks on time using agile development. Used the Robot Operating System, python and C++ to implement self-driving algorithms and simulations.}
    \resumeSubItem{Robojackets}
      {Designed and implemented a new defense strategy for Georgia Tech's autonomous robot soccer team.}
  \resumeSubHeadingListEnd
  
%-----------AWARDS-----------------
\section{Honors \& Awards}
  \resumeSubHeadingListStartBullets
    \resumeSubItem{Eagle Scout}
      {Achieved the rank of Eagle Scout through the Boy Scouts of America.}
  \resumeSubItem{Hyland Hackathon (First Place)}
      {Built an Android app that encourages exercise through a videogame.}  
  \resumeSubItem{Capital One SES Hackathon (Second Place)}
      {Built a webapp that predicts Lyft ride-sharing price surges..}      
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {Python, Java, Javascript, C++, C, Scala, MATLAB}
    \resumeSubItem{Technologies}
      {Git, Node.js, React, MySQL, MongoDB, Elasticsearch, Flask, AWS, Docker, Linux, HTML/CSS}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}